State of the Practice for Lattice Boltzmann Method Software

### 2022-01-27 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Revisions to Maintainability section (Section 3.7)

Issue tracking is used in 23 software packages, 15 of which use GitHub or GitLab
to host their git repository, seven use email, and one (SunlightLB) uses
SourceForge. Most software packages that use GitHub/GitLab have most of their
issues closed, and only three (laboetie, lettuce, Sailfish) have less than 50
percent of their issues closed. All of the top five overall ranked packages have
most of their issues closed. Alive packages (11 use issue tracking) have 64\% of
their issues closed, while dead packages (3 use issue tracking) have 71\% of
their issues closed. This information is presented in Table~\ref{gitrepodata}.
Furthermore, 13 packages that use git for version control use GitHub, while two
(Palabos, waLBerla) use GitLab. Of the other packages, one package (SunlightLB)
uses CVS for issue tracking, and seven packages do not appear to use any issue
tracking system.

@@

Figure~\ref{Fig_Maintainability} shows the maintainability ranking of the
software packages. Software packages with a high score provide version numbers
on documents and source code releases, have an abundance of high quality
artifacts, and use an issue tracking tool and version control system. These
packages also appear to reasonably handle issue tracking, having most of their
issues closed. Their code files are well commented with more than 10 percent of
the code being comments. Furthermore, four of the top 5 ranked packages are
noted as being alive.

>>>>

Issue tracking is used in 23 software packages, 15 of which use GitHub or GitLab
to host their git repository, seven use email, and one (SunlightLB) uses
SourceForge. Most software packages that use GitHub/GitLab have most of their
issues closed, and only three (laboetie, lettuce, Sailfish) have less than 50
percent of their issues closed. All of the top five overall ranked packages have
most of their issues closed. Alive packages (11 use issue tracking) have 64\% of
their issues closed, while dead packages (3 use issue tracking) have 71\% of
their issues closed. This information is presented in Table~\ref{gitrepodata}.
With respect to the host for the git repository, 13 packages use GitHub and two
(Palabos, waLBerla) use GitLab. Of the other packages, one package (SunlightLB)
uses CVS for issue tracking, and seven packages do not appear to use any issue
tracking system.

@@

Figure~\ref{Fig_Maintainability} shows the maintainability ranking of the
software packages. Software packages with a high score provide version numbers
on documents and source code releases, have an abundance of high quality
artifacts, and use an issue tracking tool and version control system. These
packages also appear to manage their issue tracking, having most of their issues
closed. Their code files are well commented with more than 10 percent of the
code being comments. Four of the top 5 ranked packages are noted as being alive.
